---
editor_options: 
  markdown: 
    wrap: 72
---

Creating a matrix with three 12 and 8 columns and calculating the means
for each column of the matrix?

```{r}
matrix(1:36, nrow = 3, ncol = 12)
```

```{r}
colMeans(matrix(1:36, nrow = 3, ncol = 12))
```

```{r}
install.packages("psych")
library(psych)

install.packages("moments")
library(moments)
```

Calculate sum, mean, median, standard deviation, skewness, quantile,
kurtosis, and variance for variable "Balance" in the job dataset

```{r}
#Sum 
sum(job$Balance)
```

```{r}
#Mean
mean(job$Balance)
```

```{r}
#Median
median(job$Balance)
```

```{r}
#Standard Deviation
sd(job$Balance)
```

```{r}
#Skewness
skewness(job$Balance)
```

```{r}
#Quantile
quantile(job$Balance)
```

```{r}
#Kurtosis
kurtosis(job$Balance)
```

```{r}
#Variance
var(job$Balance)
```

Recode the "Age" variable to three categories of "Young Adult", "Middle-
aged Adult", and "Old Adult", based on quantiles of 30%, 60%, and 80%.

```{r}
library(dplyr)
unique(job$Age)
quantile(job$Age, probs = c(.3, .6, .8))
```

```{r}
job$Age[job$Age<=33] = "Young Adult"
```

```{r}
job$Age[job$Age>33 & job$Age< 47] = "Middle-aged Adult"
```

```{r}
job$Age[job$Age>=47] = "Old Adult"
```

```{r}
View(job)
##Not quite sure what is going on in my code, as when I run the previous cell everything gets overwritten by "Old Age"
```

Sort the "Balance" variable from high to low in the job dataset and
create a new subset of the dataset with just Balance and Job
Classification variables.

```{r}
df<-job[order(-job$Balance),]
```

```{r}
View(df)
```

```{r}
df2<-subset(df, select=c(2, 4))
```

```{r}
View(df2)
```

Subset the job dataset with just the England region and with a balance
of higher than 100,000

```{r}
df3<-subset(df, df$Region == "England"& df$Balance>100000)
```

```{r}
View(df3)
```

Using the flights dataset, create a new variable using existing
variables (arr_time and sched_arr_time) and call it delay time.

```{r}
install.packages("nycflights13")
```

```{r}
library(nycflights13)
```

```{r}
View(flights)
```

```{r}
flights2<-select(flights, sched_arr_time, arr_time)
```

```{r}
View(flights2)
```

```{r}
mutate(flights2, delay_time = arr_time-sched_arr_time)
```
