---
title: "Homework 3 DATA3421"
author: "LeMaur Kydd"
date: "2023-02-22"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, include=F}
library(e1071)
library(nycflights13)
library(dplyr)
```


#### 1.) Using R, create a 3*12 matrix (3 rows and 12 columns); then calculate the means for each column of the matrix.  

```{r}
a = matrix(1:36,3,12, byrow = T)
a

a_mean = apply(a,2,mean)
a_mean
```

#### 2.Calculate sum, mean, median, standard deviation, skewness, quantile, kurtosis, and variance for variable “Balance” in the job data set.  

```{r}
job = read.csv('job.csv')
balance = job$Balance

sum(balance)
mean(balance)
median(balance)
sd(balance)
skewness(balance)
quantile(balance)
kurtosis(balance)
var(balance)
```

#### 3.Recode the “Age” variable to three categories of “Young Adult”,“Middle-aged Adult”, and “Old Adult”, based on quantiles of 30%, 60%,and 80%.  

```{r}
age = job$Age
quantile(age, probs = c(0.30,0.60,0.80))

age_categorized = cut(age,breaks = c(-Inf,33,40,47,Inf), labels = c('YoungAdult','Middle-agedAdult','OldAdult','Other'))
head(age_categorized, n = 10)
```

#### 4.Sort the “Balance” variable from high to low in the job data set and create a new subset of the data set with just Balance and Job Classification variables.  

```{r}
bal_sorted = job[order(job$Balance, decreasing = T), ]
bal_jobclass_sorted = bal_sorted[c('Balance','Job.Classification')]
head(bal_jobclass_sorted, n= 10)
```

#### 5.Subset the job data set with just the England region and with a balance of higher than 100,000.  

```{r}
job_subset = subset(job, Region == 'England' & Balance > 100000)
head(job_subset, n=10)

job_subset = job_subset[c('Region','Balance')]
head(job_subset, n=10)
```

#### 6.Using the flights data set, create a new variable using existing variables(arr_time and sched_arr_time) and call it delay time.  

```{r}
delay_time = mutate(flights, delay_time=arr_time-sched_arr_time)
head(delay_time$delay_time, n=10)
```


















