---
title: 'Homework 5'
output: html_document
date: '2023-04-24'
name: 'Alex Nanez'
---

# A: Data Visualization

## Question 1
```{r}
### Importing Libraries

library(tidyverse)
library(dplyr)
library(ggplot2)

### 1. Importing iris data set
library(datasets)
#View(iris)
str(iris)
summary(iris)
```
I loaded the **iris** data set from the datasets package and looked at its structure and summary statistics accordingly.

## Question 2
```{r}
### 2. Creating scatter plot of sepal length and width of iris flowers
#plot(iris$Sepal.Length~iris$Sepal.Width, main = 'Sepal Width vs Sepal Length',
#     xlab = 'Sepal Width', ylab = 'Sepal Length', cex.main = 1.5, cex.lab = .9,
#     cex.axis = .8)

d<-ggplot(data=iris,aes(x=Sepal.Length,y=Sepal.Width,colour=Species))
d
d+geom_point()
```

I created a scatterplot looking at the relationship between sepal length and sepal width while distinguishing the data by species.

### Question 3
```{r}
### 3. Creating box plot of petal length for each species of flower
b<-ggplot(data=iris,aes(x=Petal.Length,y=Species,colour=Species))
b+geom_boxplot()
```

I created a boxplot of the feature petal length for all 3 species of iris flowers.

## Question 4
```{r}
### 4. Creating histogram of sepal width of iris flowers
ggplot()+geom_histogram(data=iris,
                        aes(x=Sepal.Width,y=after_stat(density),fill=Species))
```

I created a histogram looking at the distribution of sepal width of the iris flowers.

# B: Linear Regression

## Question 1
```{r}
### 1. Importing mtcars data set
#help(mtcars)
#View(mtcars)
str(mtcars)
summary(mtcars)
```
I loaded the **mtcars** data set from the datasets package and explored its structure and summary statistics accordingly.

## Question 2
```{r}
### 2. Using linear regression
l<-lm(mtcars$mpg~mtcars$hp)
l
summary(l)
```
Looking at the Multiple R-squared value, 60% of variation can be explained from the hp (horsepower) feature. The regression coefficient is negative, implying a negative correlation.

## Question 3
```{r}
### 3. Using multiple linear regression model
ml<-lm(mtcars$mpg~mtcars$hp+mtcars$wt)
ml
summary(ml)
```
Looking at the Multiple R-squared value, 82.68% of variation can be explained from the hp (horsepower) and wt (weight) features.

## Question 4
```{r}
### 4. Compare the predictive power of both models
anova(l,ml) 
```
We can see that the second model performs better than the first (high F value and low significant p-value).
