---
title: "Homework 5"
author: "Jason Bard"
date: "2023-03-16"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Setup

```{r library, message = FALSE, warning = FALSE}
library(ggplot2)
library(tidyverse)
library(datasets)
library(dplyr)
```

# A: Data Visualization

## 1. Load the iris dataset into R and explore its structure and summary statistics.
```{r }
head(iris)
str(iris)
summary(iris)
```

## 2. Create a scatterplot of the sepal length and width of the iris flowers. Use different colors to represent the different species of flowers.

```{r }
ggplot(iris, aes(x = Sepal.Length, y = Sepal.Width, col = Species))+geom_point()
```

## 3. Create a boxplot of the petal length for each species of flower.

```{r }
ggplot(iris, aes(x = Petal.Length, col = Species))+geom_boxplot()
```

## 4. Create a histogram of the sepal width of the iris flowers.

```{r }
ggplot(iris, aes(x = Sepal.Width, fill = Species))+geom_histogram(bins = 10)
```

# B: Linear Regression

## 1. Load the mtcars dataset into R and explore its structure and summary statistics.

```{r }
data(mtcars)
str(mtcars)
summary(mtcars)
```

## 2. Use linear regression to model the relationship between "mpg" (dependent variable) and "hp" (Independent variable). Interpret the regression coefficients and R-squared value.

```{r }
model1 = lm(mtcars$mpg ~ mtcars$hp)
summary(model1)
```

The line that approximates the relationship between MPG and HP has a y-intercept of 30.09886 and a slope of -0.06923. This relationship has an R-squared estimate of 0.6024 and an adjusted R-squared estimate of 0.5892.

## 3. Create a multiple linear regression model (using "hp" and "wt" as Independent variables, and mpg as a dependentvariable).

```{r }
model2 = lm(data = mtcars, mpg~hp+wt)
summary(model2)
```

## 4. Compare the predictive power of the simple linear regression model (using "hp" as the predictor variable) and the multiple linear regression model (using "hp" and "wt" as predictor variables).

```{r }
anova(model1, model2)
```

The two models are different because the P-value (assuming that `P = Pr(>F)`) is less than 0.05.