---
title: "DataMining-Lab5"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# A Data Visualization
### 1. Load the iris dataset into R and explore its structure and summary statistics.
```{r}
library(tidyverse)
library(dplyr)
library(ggplot2)
library(datasets)
data(iris)
summary(iris)
str(iris)
```
### 2. Create a scatterplot of the sepal length and width of the iris flowers. Use different colors 
to represent the different species of flowers.
```{r}
scatterplot<-ggplot(data=iris, aes(x=Sepal.Length, y=Sepal.Width, colour=Species))+geom_point()+geom_smooth()+theme_classic()+labs(title = "Scatterplot of Sepal Length and Width of Iris Flowers",
       x = "Sepal Length (cm)",
       y = "Sepal Width (cm)",
       color = "Species")
scatterplot
```
### 3. Create a boxplot of the petal length for each species of flower.
```{r}
boxplotiris<- ggplot(iris, aes(x = Species, y = Petal.Length, fill = Species)) + 
  geom_boxplot() +
  labs(title = "Boxplot of Petal Length for Each Species of Flower",
       x = "Species",
       y = "Petal Length (cm)",
       fill = "Species") +
  theme_classic()
boxplotiris
```

### 4. Create a histogram of the sepal width of the iris flowers.

```{r}
histiris <- ggplot(iris, aes(x = Sepal.Width, fill = Species)) + 
  geom_histogram(binwidth = 0.2, alpha = 0.5, position = "identity") +
  labs(title = "Histogram of Sepal Width of Iris Flowers",
       x = "Sepal Width (cm)",
       y = "Frequency",
       fill = "Species") +
  scale_fill_manual(values = c("#00AFBB", "#E7B800", "#FC4E07")) +
  theme_classic()
histiris
```

# B: Linear Regression
### 1. Load the mtcars dataset into R and explore its structure and summary statistics.

```{r}

data(mtcars)
summary(mtcars)
str(mtcars)
```
### 2. Use linear regression to model the relationship between "mpg" (dependent variable) and "hp" (Independent variable). Interpret the regression coefficients and R-squared value.

```{r}
linear_model <- lm(mpg~hp, data=mtcars)
summary(linear_model)
```
#### Using the linear regression, we can see that the intercept is 30.099 and the regression coefficient is -0.068, which means that mpg and hp have negative correlation. The R-square is 0.6024, about 60% variability can be seen in the model. 

### 3. Create a multiple linear regression model (using "hp" and "wt" as Independent variables, and mpg as a dependent variable).

```{r}
model1 <- lm(mpg~hp+wt, data=mtcars)
summary(model1)
```
### 4. Compare the predictive power of the simple linear regression model (using "hp" as the predictor variable) and the multiple linear regression model (using "hp" and "wt" as predictor variables).

```{r}
anova(linear_model,model1)
```
#### From the above comparison, we can see that the P-value is << 0.05, we can say that there is difference between predictive power of the model. 
