# A: Data Visualization
## Question 1
Load the iris dataset into R and explore its structure and summary statistics.
```{r}
library(datasets)

# Loads the iris dataset
data(iris)

# Dataset structure of the iris dataset
str(iris)

# Summary statistics of the iris dataset
summary(iris)
```

## Question 2
Create a scatterplot of the sepal length and width of the iris flowers. Use different colors to represent the different species of flowers.

```{r}
library(ggplot2)
ggplot(data = iris, aes(x = Sepal.Length, y = Sepal.Width, color = Species)) +
  geom_point() +
  ggtitle("Scatterplot of Sepal Length and Width") +
  xlab("Sepal Length") +
  ylab("Sepal Width")
```

## Question 3
Create a boxplot of the petal length for each species of flower.
    
```{r}
ggplot(data = iris, aes(x = Species, y = Petal.Length)) +
  geom_boxplot() +
  ggtitle("Boxplot of Petal Length by Species") +
  xlab("Species") +
  ylab("Petal Length")
```

## Question 4
Create a histogram of the sepal width of the iris flowers

```{r}
ggplot(data = iris, aes(x = Sepal.Width, fill = Species)) +
  geom_histogram(binwidth = 0.2, alpha = 0.5, position = "identity") +
  ggtitle("Histogram of Sepal Width") +
  xlab("Sepal Width") +
  ylab("Frequency")
```

# B: Linear Regression
## Question 1
Load the mtcars dataset into R and explore its structure and summary statistics.

```{r}
data(mtcars)

# Dataset structure of the mtcars dataset
str(mtcars)

# Summary statistics of the mtcars dataset
summary(mtcars)
```

## Question 2
Use linear regression to model the relationship between "mpg" (dependent variable) and "hp" (Independent variable). Interpret the regression coefficients and R-squared value.

```{r}
# Linear regression model
model1 <- lm(mpg ~ hp, data = mtcars)
summary(model1)
```

## Question 3
3. Create a multiple linear regression model (using "hp" and "wt" as Independent variables, and mpg as a dependent variable).
    
```{r}
model2 <- lm(mpg ~ hp + wt, data = mtcars)
summary(model2)
```

## Question 4
Compare the predictive power of the simple linear regression model (using "hp" as the predictor variable) and the multiple linear regression model (using "hp" and "wt" as predictor variables).
    
```{r}
# Simple linear regression model
predict1 <- predict(model1)

# Multiple linear regression model
predict2 <- predict(model2)

# Root mean squared error
rmse1 <- sqrt(mean((predict1 - mtcars$mpg)^2))
rmse2 <- sqrt(mean((predict2 - mtcars$mpg)^2))

# Print the RMSE values
rmse1
rmse2
```