---
title: "Data3421-Lab5-MonicaCortez"
output: html_document
date: "2023-03-11"
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

library(tidyverse)
library(dplyr)
library(ggplot2)
library(datasets)

#3A: Data Visualization

#1. Load the iris dataset into R and explore its structure and summary statistics.

```{r }
head(iris)
str(iris)
summary(iris)
```


#2. Create a scatterplot of the sepal length and width of the iris flowers. Use different colors to represent the different species of flowers.

```{r }
ggplot(iris) +aes(x = Sepal.Length, y = Petal.Length, col = Species) +geom_point() +scale_color_hue()
```


#3 Create a boxplot of the petal length for each species of flower.

```{r }
box.plot<-ggplot(iris)+aes(Petal.Length, col = Species) +geom_boxplot() +scale_color_hue()
box.plot


#3 Create a boxplot of the petal length for each species of flower.
```{r }
box.plot<-ggplot(iris)+aes(Petal.Length, col = Species) +geom_boxplot() +scale_color_hue()
box.plot
```


#4. Create a histogram of the sepal width of the iris flowers.
```{r }
ggplot(iris)+aes(x=Sepal.Length,fill=Species) + geom_histogram() +theme_minimal()
```


##B: Linear Regression:

#1 Load the mtcars dataset into R and explore its structure and summary statistics.
```{r }
data("mtcars")
head(mtcars)
summary(mtcars)
```


#2Use linear regression to model the relationship between "mpg" (dependent variable) and "hp" (Independent variable). Interpret the regression coefficients and R-squared value.
```{r }

install.packages("QuantPsyc")
library(QuantPsyc)

modelone<-lm(data=mtcars,mpg~hp)
modelone
summary(modelone)
```

#Coeffiecent is -0.06823.
#R-squared value is 0.6024 and the adjusted R-squared is 0.5892. modelone contains about 60 percent variability.  
#Intercept is 30.09886

#3. Create a multiple linear regression model (using "hp" and "wt" as Independent variables,and mpg as a dependent variable).

```{r }
modeltwo<-lm(data=mtcars, mpg~hp+wt)
modeltwo
summary(modeltwo)
```


#4. Compare the predictive power of the simple linear regression model (using "hp" as the predictor variable) and the multiple linear regression model (using "hp" and "wt" as predictor variables).

```{r }
anova(model1,model2)
```

# Simple linear regression and multiple linear regression models predictive power is different as the p-value is less 0.05.