---
title: "Lab5"
output: html_document
date: "2023-03-09"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Lab 5

This is my markdown file for lab 5. In this file you will see all of the work I did on this assignment and my solutions for it.


### Imports
```{r imports}
library(ggplot2)
library(datasets)
```


## Part A

### Loading in and getting the summary statistics for the iris dataset
```{r iris}
data(iris)
summary(iris)
```

### Plots for the iris dataset
#### Scatter Plot

```{r scatter, echo=TRUE}
d<-ggplot(data = iris,aes(x=Sepal.Length,y=Sepal.Width, color = Species))
d+geom_point()+geom_smooth(alpha=0.01)+theme_classic()
```

#### Box Plot
```{r Box, echo=TRUE}
b<-ggplot(data = iris,aes(x=Petal.Length, color = Species))
b+geom_boxplot(size=2,outlier.color = "Purple",outlier.shape = 2,
               outlier.size = 1,outlier.alpha = 0.4,)+theme_classic()+coord_flip()
```

#### Histogram

```{r Hist, echo=TRUE}
ggplot()+geom_histogram(data = iris,aes(x=Sepal.Width,y=..density.., fill = Species),
                        color="black")+theme_linedraw()
```

## Part B

### Loading in and getting the summary statistics for the mtcars dataset
```{r mtcars}
data("mtcars")
summary(mtcars)
```


### Use linear regression to model the relationship between "mpg" (dependent variable) and "hp" (Independent variable). and Interpret the regression coefficients and R-squared value.

```{r linmod}
carmod<-lm(mtcars$mpg~mtcars$hp)

carmod$coefficients
```

### Create a multiple linear regression model (using "hp" and "wt" as Independent variables, and mpg as a dependentvariable).
```{r multlinmod}
multcarmod<-lm(mtcars$mpg~mtcars$hp+mtcars$wt)
multcarmod$coefficients
```



### Comparing the predictive power of the simple linear regression model (using "hp" as the predictor variable) and the multiple linear regression model (using "hp" and "wt" as predictor variables).


```{r comparison}
anova(carmod,multcarmod)

plot(carmod)

plot(multcarmod)
```

