---
title: "H5-Shashwat"
output: html_document
date: "2023-03-06"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Homework 5
### A
#### 1. Load the iris dataset into R and explore its structure and summary statistics.

```{r }
library(tidyverse)
library(dplyr)
library(ggplot2)
library(datasets)
data(iris)
summary(iris)
str(iris)
```

#### 2. Create a scatterplot of the sepal length and width of the iris flowers. Use different colors to represent the different species of flowers.

```{r }
names(iris)
s<-ggplot(data=iris, aes(x=Sepal.Length, y=Sepal.Width, colour=Species))
s
s+geom_point()+geom_smooth()+theme_classic()
```

#### 3. Create a boxplot of the petal length for each species of flower.

```{r }
b<-ggplot(data=iris, aes(Petal.Length, colour=Species))
b
b+geom_boxplot(outlier.color = "black")+theme_classic()
View(iris)
```

#### 4. Create a histogram of the sepal width of the iris flowers.

```{r }
ggplot()+geom_histogram(data=iris,aes(x=Sepal.Width,y=..density..,fill=Species),color='black')+theme_linedraw()
```

### B

#### 1. Load the mtcars dataset into R and explore its structure and summary statistics.

```{r }
data(mtcars)
summary(mtcars)
str(mtcars)
names(mtcars)
```
#### 2. Use linear regression to model the relationship between "mpg" (dependent variable) and "hp" (Independent variable). Interpret the regression coefficients and R-squared value.
```{r }
library(QuantPsyc)
model1<-lm(mpg~hp,data = mtcars)
model1
summary(model1)
```
##### The intercept is 30.1. It means that the predicted mpg for hp=0 is 30.1
##### The coefficient -0.068 is the slope of the model. For a unit increase in hp, the mpg decreases by -0.068.
##### The r-squared value 0.6 can explain 60% variability in the model.

#### 3. Create a multiple linear regression model (using "hp" and "wt" as Independent variables, and mpg as a dependent variable).

```{r }
model2<-lm(mpg~hp+wt,data=mtcars)
model2
summary(model2)
```
#### 4. Compare the predictive power of the simple linear regression model (using "hp" as the predictor variable) and the multiple linear regression model (using "hp" and "wt" as predictor variables).

```{r }
anova(model1,model2)
```
##### The model has a p-value less than 0.05, which means there is a difference in the predictive power of the models.
