---
title: "Lab5Markdown"
output: html_document
date: "2023-03-07"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## DATA VISUALIZATION

##### 1. Load the iris dataset into R and Explore its structure and summary statistics

```{r}
# Loading the dataset

data(iris)
```


```{r echo = FALSE, result = 'asis'}

# Loading the dataset

data(iris)
library(knitr)
kable(iris [1:5,])
```

```{r iris}

# Exploring its structure

str(iris)

# Exploring its summary statistic

summary(iris)
```


##### 2. Create a scatterplot of the sepal length and width of the iris flowers. Use different colors to represent the different species of flowers.


```{r}
# Create scatterplot with customized labels, colors, and design elements
library(ggplot2)
ggplot(iris, aes(x = Sepal.Length, y = Sepal.Width, color = Species)) +
  geom_point(size = 3, alpha = 0.8) +
  labs(x = "Sepal Length (cm)", y = "Sepal Width (cm)",
       title = "Scatterplot of Sepal Length vs. Width",
       subtitle = "Grouped by Species",
       color = "Species") +
  theme_bw() +
  theme(plot.title = element_text(size = 16, face = "bold", hjust = 0.5),
        plot.subtitle = element_text(size = 14, hjust = 0.5),
        axis.text = element_text(size = 12),
        axis.title = element_text(size = 14),
        legend.title = element_text(size = 12),
        legend.text = element_text(size = 10),
        legend.position = "bottom")
```


##### 3. Create a boxplot of the petal length for each species of flower.

```{r}
# Creating Boxplot
library(ggplot2)

ggplot(iris, aes(x = Species, y = Petal.Length)) +
  geom_boxplot() +
  labs(x = "Species", y = "Petal Length")

```


##### 4. Create a histogram of the sepal width of the iris flowers.


```{r}
# Creating Histogram
library(ggplot2)

ggplot(iris, aes(x = Sepal.Width)) +
  geom_histogram(binwidth = 0.2, color = "black", fill = "green") +
  labs(x = "Sepal Width", y = "Frequency")


```



## LINEAR REGRESSION

##### 1. Load the mtcars dataset into R and Explore its structure and summary statistics

```{r echo = FALSE, result = 'asis'}

# Loading the dataset

data(mtcars)
library(knitr)
kable(mtcars [1:5,])
```

```{r mtcars}
# Exploring its structure:
str(mtcars)

# Exploring its summary statistic:
summary(mtcars)
```


##### 2. Use linear regression to model the relationship between "mpg" (dependent variable) and "hp" (Independent variable). Interpret the regression coefficients and R-squared value

```{r}
# fit linear regression model
fit_LRM <- lm(mpg ~ hp, data = mtcars)

# display summary of the model
summary(fit_LRM)

```

##### 3. Create a multiple linear regression model (using "hp" and "wt" as Independent variables, and mpg as a dependent variable).

```{r}
# fit multiple linear regression model
fit_MLRM <- lm(mpg ~ hp + wt, data = mtcars)  

# display summary of the model
summary(fit_MLRM)  
```


##### 4. Compare the predictive power of the simple linear regression model (using "hp" as the predictor variable) and the multiple linear regression model (using "hp" and "wt" as predictor variables).

```{r}
# loading mtcars dataset
data(mtcars)

# Fit simple linear regression model using hp as predictor variable
fit1 <- lm(mpg ~ hp, data = mtcars)

# Fit multiple linear regression model using hp and wt as predictor variables
fit2 <- lm(mpg ~ hp + wt, data = mtcars)

# Making predictions using simple and multiple regression models
pred1 <- predict(fit1, newdata = mtcars)
pred2 <- predict(fit2, newdata = mtcars)

# Calculating mean squared error (MSE) and root mean squared error (RMSE)
MSE1 <- mean((mtcars$mpg - pred1)^2)
MSE2 <- mean((mtcars$mpg - pred2)^2)
RMSE1 <- sqrt(MSE1)
RMSE2 <- sqrt(MSE2)

# Calculating R-squared values
Rsq1 <- summary(fit1)$r.squared
Rsq2 <- summary(fit2)$r.squared

# Display evaluation metrics
cat("Simple Linear Regression Model:\n")
cat("MSE:", MSE1, "\n")
cat("RMSE:", RMSE1, "\n")
cat("R-squared:", Rsq1, "\n\n")

cat("Multiple Linear Regression Model:\n")
cat("MSE:", MSE2, "\n")
cat("RMSE:", RMSE2, "\n")
cat("R-squared:", Rsq2, "\n")
```




